---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# mzAnnotation

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/jasenfinch/mzAnnotation/workflows/R-CMD-check/badge.svg)](https://github.com/jasenfinch/mzAnnotation/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/jasenfinch/mzAnnotation/devel.svg)](https://codecov.io/github/jasenfinch/mzAnnotation?branch=devel)
[![DOI](https://zenodo.org/badge/33083554.svg)](https://zenodo.org/badge/latestdoi/33083554)
<!-- badges: end -->


An R package containing tools for putative annotation of accurate m/z from electrospray ionisation mass spectrometry data.

### Installation

To install run:

```R
devtools::install_github('jasenfinch/mzAnnotation')
```

### Tools

Available tools include:

```{r,echo=FALSE}
library(mzAnnotation)
```

* Adduct, isotope and biotransfromation relationship prediction

```{r}
res <- relationshipCalculator(c(132.03023,168.00691))

res
```

* Molecular formula generation

```{r}
res <- generateMF(342.11621,
                  element_max = c(C = 12,H = 22,N = 0,
                                  O = 11,P = 0,S = 0))
res
```

* Isotope distribution calculation

```{r}
res <- isotopeDistribution(MF = 'C4H5O5',charge = -1)
res
```

* Putative ionisation product searches

```{r}
db <- metaboliteDB(amino_acids,descriptors(amino_acids$SMILES))
res <- PIPsearch(db = db,
                 mz = 132.03023,
                 ppm = 5,
                 adduct = '[M-H]1-',
                 isotope = NA)
res
```
